---
title: Blogdown notes and intro
author: |
 | Matthew Malishev^1^*
 | _^1^ Department of Biology, Emory University, 1510 Clifton Road NE, Atlanta, GA, USA, 30322_
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
fontsize: 10
geometry: margin=1in
documentclass: article
linkcolor: pink
urlcolor: blue
citecolor: red
output:
  pdf_document:
    includes:
      in_header: # add .tex file with header content
    highlight: tango
    template: null
    toc: yes
    toc_depth: 3
    number_sections: false
    fig_width: 4
    fig_height: 5
    fig_caption: true
    df_print: tibble 
    citation_package: biblatex # natbib
    latex_engine: xelatex #pdflatex # lualatex
    keep_tex: true # keep .tex file in dir 
  html_document:
    highlight: tango
    code_folding: hide
    toc: yes
    toc_depth: 3
    number_sections: no
    toc_float: yes
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
inludes:
  before_body: before_body.tex
subtitle: 
tags:
- nothing
- nothingness
params: 
  dir: "/Users/malishev/Documents/Melbourne Uni/Programs/blogdown/"  #wd
  date: !r Sys.Date()
  version_R: !r getRversion()
  version_hugo: !r blogdown::hugo_version() 
  email: "matthew.malishev@gmail.com"
  doi: https://github.com/darwinanddavis/blogdown/
classoption: portrait
# ^['https://github.com/darwinanddavis/blogdown'] # footnote
vignette: >
  %\VignetteIndexEntry{blogdown notes}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small"
)
```

\  

Date: `r params$date`  
R version: `r params$version_R`   
Hugo version: `r params$version_hugo`  
*Corresponding author: `r params$email`  
This document can be found at `r params$doi`  

\newpage  

## Overview  

Notes on using `blogdown` and `hugo` for website development.  

### Links  
Guide to hugo: https://gohugo.io/getting-started/quick-start/  
Hugo themes: https://themes.gohugo.io/  
Intro to blogdown: https://bookdown.org/yihui/blogdown/  

### Install  
```{r, load packages, include=T, cache=T, message=F, warning=F, results='hide'}
packages <- c("blogdown")   
if (require(packages)) {
    install.packages(packages,dependencies = T)
    blogdown::install_hugo() # install hugo
    require(packages)
}
lapply(packages,library,character.only=T)

# -------- Hugo --------
# check version
blogdown::hugo_version()
# update version. latest versions: https://github.com/gohugoio/hugo/releases
blogdown::update_hugo()
```

### Create local root directory 
```{r}
setwd(params$dir)
getwd()
```

### Set theme  
```{r}
# generate new site. Replaces File > New Project > Website using blogdown 
theme <- "eddiewebb/hugo-resume"
```

### Generate site  
```{r}
blogdown::new_site(theme = theme)
blogdown::build_site()
```

### Troubleshooting  
```{r help}
#help
?blogdown::new_site
```

### Directories and files  
Guide: https://bookdown.org/yihui/blogdown/a-quick-example.html  
- config.toml: specify some global settings for your site  
- ~ contents/: where you write the R Markdown or Markdown source files for your posts and pages  
- ~public/: The publishing directory (by default, public/). Your website will be generated to this directory   

### Live preview  
```{r}
blogdown::serve_site()
```

### Globals
- blogdown.subdir: A subdirectory under content/  
- blogdown.yaml.empty:	Preserve empty fields in YAML?  
- options(blogdown.author = 'Matt Malishev', blogdown.ext = 'Rmd')  

### Create new post
```{r}
# posts appear under ~/content/post/
blogdown:::new_post_addin() # create new post
blogdown:::update_meta_addin() # update post metadata 
```

### Publish site  
```{r}
# creates ~public/ dir
blogdown::hugo_build() 
```

### Next steps  
1. Create a new site on Netlify from your GitHub repository that contains the source files of your website   





